---
title: 'TidyTuesday:  Number of World Heritage sites'
author: "Akhapwoya"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: '6'
  html_document:
    df_print: paged
    toc: true
    toc_depth: '6'
urlcolor: blue
subtitle: "2024/2024-02-06"
---

\newpage

```{r, include=FALSE}
knitr::opts_chunk$set(
    echo = T, warning=FALSE, message=FALSE, attr.source='.numberLines', 
    attr.output='.numberLines', fig.align='center', dpi=450, 
    fig.width=10, fig.height=10)
```

# Introduction

This week we're exploring a very small subset of [UNESCO World Heritage Sites](https://whc.unesco.org/en/list). 
The [1 dataset, 100 visualizations project](https://100.datavizproject.com/) used this dataset to explore different ways of visualizing a simple dataset.

# EDA

```{r}
library(readr)
library(RColorBrewer)
```


```{r, eval=FALSE}
heritage <- read_csv("heritage.csv")
```

## The Data

### Data Dictionary

1. country: Country
2. 2004: Number of UNESCO World Heritage sites in 2004
3. 2022: Number of UNESCO World Heritage sites in 2022

```{r, eval=FALSE}
# Option 1: tidytuesdayR package 
## install.packages("tidytuesdayR")

tuesdata <- tidytuesdayR::tt_load('2024-02-06')
```


```{r, eval=TRUE}
## OR
tuesdata <- tidytuesdayR::tt_load(2024, week = 6)
heritage <- tuesdata$heritage
```


```{r, eval=FALSE}
# Option 2: Read directly from GitHub
heritage <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-02-06/heritage.csv')
```


\newpage
## Stacked bar chart of the number of World Heritage sites in Denmark, Norway and Sweden in 2004 and 2022

There are more sites in each country in 2022 than 2004, 4 and 10 in Denmark, 5 and 8 in Norway, 13 and 15 in Sweden respectively.

```{r}
# png("bar1.png", height=15, width=15, units="cm", res = 300)
barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,
  legend.text=heritage$country,
  args.legend=list(bty="n",horiz=TRUE),
  col=brewer.pal(3,"Set1"),
  border="white",ylim=c(0,20),
  #ylab="",
  main="number of World Heritage sites")
box(bty="l")
# dev.off()
```


```{r}
# png("bar2.png", height=15, width=15, units="cm", res = 300)
barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,horiz=TRUE,
  legend.text=heritage$country, 
  args.legend=list(bty="n"),
  col = brewer.pal(3,"Set1"),border="white",
  xlim=c(0,20), 
  #xlab="",
  main="number of World Heritage sites")
box(bty="l")
# dev.off()
```


```{r}
# png("bar3.png", height=15, width=15, units="cm", res = 300)
x = barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,
  legend.text = heritage$country, 
  args.legend=list(bty="n",horiz=TRUE),
  col=brewer.pal(3,"Set1"),border="white",
  ylim=c(0,20),
  main="number of World Heritage sites")
y = as.matrix(heritage[,2:3])
text(x,y-3,labels=as.character(y))
# dev.off()
```


```{r, eval=FALSE}
png("bar1.png", height=15, width=15, units="cm", res = 300)
barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,
  legend.text=heritage$country,
  args.legend=list(bty="n",horiz=TRUE),
  col=brewer.pal(3,"Set1"),
  border="white",ylim=c(0,20),
  #ylab="",
  main="number of World Heritage sites")
box(bty="l")
dev.off()
#
png("bar2.png", height=15, width=15, units="cm", res = 300)
barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,horiz=TRUE,
  legend.text=heritage$country, 
  args.legend=list(bty="n"),
  col = brewer.pal(3,"Set1"),border="white",
  xlim=c(0,20), 
  #xlab="",
  main="number of World Heritage sites")
box(bty="l")
dev.off()
#
png("bar3.png", height=15, width=15, units="cm", res = 300)
x = barplot(
  as.matrix(heritage[,2:3]), beside=TRUE,
  legend.text = heritage$country, 
  args.legend=list(bty="n",horiz=TRUE),
  col=brewer.pal(3,"Set1"),border="white",
  ylim=c(0,20),
  main="number of World Heritage sites")
y = as.matrix(heritage[,2:3])
text(x,y-3,labels=as.character(y))
dev.off()
#
```

