---
title: "Bobs Burgers"
format: html
editor: visual
knitr:
  opts_chunk: 
    collapse: true
    comment: "#>"
    warning: false
    message: false
    R.options:
      knitr.graphics.auto_pdf: true
---

```{r, echo=F}
knitr::opts_chunk$set( echo = T, warning=FALSE, message=FALSE, attr.source='.numberLines', attr.output='.numberLines', fig.align='center', dpi=700, fig.width=20, fig.height=10)
```

\newpage

## Introduction

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(stringr)
library(ggrepel)
```

## Data

### Data Dictionary

Data is contained in the `episode_metrics.csv`

| variable | class | description |
|:-----------------|:---------------|:-------------------------------------|
| season | integer | The season number in which the episode is part of the Bob's Burgers TV show. |
| episode | integer | The episode number within the specific season of Bob's Burgers. |
| dialogue_density | double | The number of non-blank lines in this episode. |
| avg_length | double | The average number of characters (technically codepoints, see `?stringr::str_length`) per line of dialogue. |
| sentiment_variance | double | The variance in the numeric AFINN sentiment of words in this episode. See `?textdata::lexicon_afinn` for further information. |
| unique_words | integer | The number of unique lowercase words in this episode. |
| question_ratio | double | The proportion of lines of dialogue that contain at least one question mark ("?"). |
| exclamation_ratio | double | The proportion of lines of dialogue that contain at least one exclamation point ("!"). |


```{r}
episode_metrics <- read_csv("episode_metrics.csv")
head(episode_metrics)
```

### EDA

```{r}
season_episode_que_excl_labs = episode_metrics |>
  select(season, episode, question_ratio,exclamation_ratio) |>
  filter(question_ratio > 0.25 | exclamation_ratio > 0.25) |>
  mutate(
    ssn_eps = str_c("Season: ", season, ", Episode: ", episode, sep = '')
  )
```


```{r}
bobs_burger_exclamation_question_ratios_plot = episode_metrics |>
  ggplot(aes(x = question_ratio, y = exclamation_ratio)) +
  geom_point() +
  geom_point(
    data = season_episode_que_excl_labs,
    aes(
      x = question_ratio, y = exclamation_ratio,
      color = ssn_eps)
  ) +
  geom_text_repel(
    data = season_episode_que_excl_labs,
    aes(
      x = question_ratio, y = exclamation_ratio,
      label = ssn_eps, color = ssn_eps), nudge_x = 0.001, nudge_y = 0.001) +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal() +
  labs(
    title = "Bob's Burgers",
    subtitle = "The proportion of lines of dialogue that contain at least one exclamation point ('!') ~ least one question mark ('?')",
    x = "Question Ratio", y = "Exclamation Ratio",
    caption = c("tidytuesdayR::tt_load(2024, week = 47)", "https://github.com/akhapwoyaco/")
  ) +
  theme(
    axis.text = element_text(face = 'bold'),
    axis.title = element_text(face = 'bold'),
    plot.title = element_text(face = 'bold', hjust = 0.5),
    plot.subtitle = element_text(face = 'bold', hjust = 0.5, size = rel(0.75)),
    legend.position = 'none',
    legend.title = element_blank(),
    legend.background = element_blank(),
    legend.direction = 'horizontal',
    plot.caption = element_text(hjust = c(1,0))
  )
```


```{r}
bobs_burger_exclamation_question_ratios_plot
```

### Save Plot

```{r}
ggsave(
  filename = "bobs_burger_exclamation_question_ratios_plot.jpeg",
  plot = bobs_burger_exclamation_question_ratios_plot,  dpi = 600,
  width = 30, height = 25, units = 'cm'
)
```

